---
title: "De Correspondent YouTube Extremism Research"
output: html_notebook
---

This document describes a proposal for a coherent methodology for researching to what degree the YouTube recommendation system leads people to more extreme content.

```{r}
# Data reading and converting packages
library(tidyverse)
library(stringr)
library(purrr)
library(jsonlite) # https://cran.r-project.org/web/packages/jsonlite/jsonlite.pdf

# YouTube API package
library(tuber) # https://cloud.r-project.org/web/packages/tuber/tuber.pdf
# Usint the tuber package to access the YouTube API
# http://soodoku.github.io/tuber/index.html
yt_oauth(app_id = Sys.getenv("YT_CLIENT_ID"), app_secret = Sys.getenv("YT_CLIENT_SECRET"), token = "")

# Network graph packages
require(devtools)
library(readgdf) # https://github.com/mikajoh/readgdf
library(igraph) # http://igraph.org/r/
library(networkD3) # https://cran.r-project.org/web/packages/networkD3/networkD3.pdf

# Text Analysis packages
library(quanteda)
library(topicmodels)

# Parallel computing
library(parallel)
```

# Identifying extreme organisations; 'left' and 'right'

We started with compiling a list of extreme organizations (media, political parties, ngo’s, think tanks). Sources we used were Kafka (a Dutch anti fascist organization), Wikipedia and academic literature. We focused on European organizations and added some well known US YouTube channels.

```{r}
# Let's take a smaller sample while refining the methodology
sample_size <- 0.05
# Reading in list of seed channels; those identified as extreme left or right
right_channels <- read_csv("Local extremism data/Seed list extreme channels.csv")
dim(right_channels)
sample_right_channels <- sample_frac(right_channels, size = sample_size)
dim(sample_right_channels)
right_channels <- sample_right_channels # To be removed when switching to whole dataset

left_channels <- read_csv("Local extremism data/lefty_seeds.csv")
dim(left_channels)
sample_left_channels <- sample_frac(left_channels, size = sample_size)
dim(sample_left_channels)
left_channels <- sample_left_channels # To be removed when switching to whole dataset

# Extracting channeld Ids only
right_channel_IDs <- right_channels$Id 
left_channel_IDs <- left_channels$Id
```

## TO DO Removing wrongly identified extreme channels
- Game channels


## Acquiring channel details

Through the YouTube API we acquire channel details.

```{r message=FALSE}

# Function to gather channel information by ID

gather_channel_details <- function(channel_ID){

  # Channel content details
  safe_channel_resources <- safely(list_channel_resources)
  channel_content <- safe_channel_resources(filter = c(channel_id = channel_ID), part = "contentDetails")
  print("Channel content details")
  str(channel_content)
  
  # Channel topic details
  channel_topics <- safe_channel_resources(filter = c(channel_id = channel_ID), part = "topicDetails")
  print("Channel topic details")
  str(channel_topics)
  
  # Channel statistics
  safe_channel_stats <- safely(get_channel_stats)
  channel_statistics <- safe_channel_stats(channel_id = channel_ID)
  print("Channel statistics")
  str(channel_statistics)
  
  # Channel playlists
  safe_playlists <- safely(get_playlists)
  channel_playlists <- safe_playlists(filter = c(channel_id = channel_ID))
  print("Channel playlists")
  str(channel_playlists)
  
  # Channel comments threads
  safe_comment_threads <- safely(get_comment_threads)
  channel_comment_threads <- safe_comment_threads(filter = c(channel_id = channel_ID), max_results = 101)
  print("Channel comment threads")
  str(channel_playlists)
  
  # Channel subscriptions
  safe_subscriptions <- safely(get_subscriptions)
  channel_subscriptions <- safe_playlists(filter = c(channel_id = channel_ID))
  print("Channel subscriptions")
  str(channel_subscriptions)
  
  # Channel videos
  safe_channel_videos <- safely(list_channel_videos)
  channel_videos <- safe_channel_videos(channel_id = channel_ID, max_results = 51)
  channel_video_IDs <- as.character(channel_videos$result$contentDetails.videoId)
  print("Channel video IDs")
  str(channel_video_IDs)
  
  # Return list of results
  list(channel_content = channel_content,
       channel_topics = channel_topics,
       channel_statistics = channel_statistics,
       channel_playlists = channel_playlists,
       channel_comment_threads = channel_comment_threads,
       channel_subscriptions = channel_subscriptions,
       channel_videos = channel_videos)

}

# Gathering channel details using parallel processing

cl <- makeCluster(10)

clusterEvalQ(cl, {library(purrr)
                  library(tuber)})
clusterEvalQ(cl, yt_oauth(app_id = Sys.getenv("YT_CLIENT_ID"), app_secret = Sys.getenv("YT_CLIENT_SECRET"), token = ""))

system.time(left_channel_details <- parLapply(cl, left_channel_IDs, gather_channel_details))
# system.time(right_channel_details <- parLapply(cl, right_channel_IDs, gather_channel_details))

stopCluster(cl)
```

# Extracting required details and building channel video lookup

```{r}
## Create simplified data frames

# Channel-video lookup data frame
channel_videos_df <- data.frame(matrix(ncol = 2))
names(channel_videos_df) <- c("channel_id", "video_id")
channel_videos_df$channel_id <- as.character(channel_videos_df$channel_id)
channel_videos_df$video_id <- as.character(channel_videos_df$video_id)

# Function to simplify channel output and build channel-video lookup table
simplify_channel_details <- function(channel_details_list){
  
  # Channel details
  channel_df <- data.frame(matrix(ncol = 3, nrow = length(channel_details_list)))
  names(channel_df) <- c("channel_id", "channel_title", "channel_description")
  str(channel_df)
  
  # Extract channel details
  for (i in seq_along(channel_details_list)){
    print(paste("Processing channel index: ", i))
    tryCatch(channel_df[i, "channel_id"] <- channel_details_list[[i]]$channel_content$result$items[[1]]$id, error = function(e) print("Error"))
    tryCatch(channel_df[i, "channel_title"] <- channel_details_list[[i]]$channel_statistics$result$snippet$title, error = function(e) print("Error"))
    tryCatch(channel_df[i, "channel_description"] <- channel_details_list[[i]]$channel_statistics$result$snippet$description, error = function(e) print("Error"))
  }
  
  # Extend channel-video lookup data frame
  channel_videos <- data.frame(matrix(ncol = 2, nrow = length(channel_details_list[[1]]$channel_videos$result$contentDetails.videoId)))
  names(channel_videos) <- c("channel_id", "video_id")
  print("Channel videos")
  str(channel_videos)
  
  channel_videos$channel_id <- as.character(channel_details_list[[1]]$channel_content$result$items[[1]]$id)
  channel_videos$video_id <- as.character(channel_details_list[[1]]$channel_videos$result$contentDetails.videoId)
  
  print("Channel videos data frame:")
  str(channel_videos_df)
  
  list(channel_df, channel_videos)
}

# Simplify channel output
simplified_left_data <- simplify_channel_details(left_channel_details)
left_channels_data <- simplified_left_data[[1]]
channel_videos_df <- rbind(channel_videos_df, simplified_left_data[[2]])

#simplified_right_data <- simplify_channel_details(right_channel_details)
#right_channels_data <- simplified_right_data[[1]]

channel_videos_df <- rbind(channel_videos_df, simplified_right_data[[2]])

# Store buffer data
saveRDS(left_channels_data, file = "left_channels_data.rds")
saveRDS(channel_videos_df, file = "channel_videos.rds")
```

## Filtering channels

Based on categories...

## Gathering video details

```{r}
# To avoid double downloading identify unique videos

unique_video_IDs <- unique(channel_videos_df$video_id)[-1]
str(unique_video_IDs)

# Function to gather video details by ID

gather_video_details <- function(video_ID){
  
  video_id <- video_ID
  
  # Video information
  safe_video_details <- safely(get_video_details)
  video_details <- safe_video_details(video_id = as.character(video_ID))
  print("Video details")
  str(video_details)
  
  # Video tags
  video_tags <- unlist(video_details$items[[1]]$snippet$tags)
  print("Video tags")
  str(video_tags)

  # Video caption tracks
  safe_caption_tracks <- safely(list_caption_tracks)
  video_tracks <- safe_caption_tracks(video_id = as.character(video_ID))
  print("Video caption tracks")
  str(video_tracks)
  
  # Video captions
  safe_captions <- safely(get_captions)
  video_captions <- safe_captions(id = as.character(video_tracks$result$id), tlang = "en") # WHICH TRACK TO TAKE?
  print("Video captions")
  str(video_captions)
  
  # Video comment thread
  safe_comments <- safely(get_comment_threads)
  video_comments <- safe_comments(filter = c(video_id = as.character(video_ID)), max_results = 101)
  print("Video comments")
  str(video_comments)
  
  # Return list of results
  list(video_id = video_id, video_details = video_details, video_tags = video_tags, video_tracks = video_tracks, video_captions = video_captions, video_comments = video_comments)
  
}

# Gather unique video details

cl <- makeCluster(10)

clusterEvalQ(cl, {library(purrr)
                  library(tuber)})
clusterEvalQ(cl, yt_oauth(app_id = Sys.getenv("YT_CLIENT_ID"), app_secret = Sys.getenv("YT_CLIENT_SECRET"), token = ""))

system.time(video_details <- parLapply(cl, unique_video_IDs, gather_video_details))

stopCluster(cl)

# Simplify video details output

simplify_video_details <- function(video_details_list){
  
  # Video details
  video_df <- data.frame(matrix(ncol = 6, nrow = length(video_details_list)))
  names(video_df) <- c("video_id", "video_title", "video_description", "video_tags", "video_transcript", "video_comments")
  
  # Extract channel details
  for (i in seq_along(video_details_list)){
    video_df[i, "video_id"] <- video_details_list[[i]]$video_id
    video_df[i, "video_title"] <- video_details_list[[i]]$video_details$result$items[[1]]$snippet$title
    video_df[i, "video_description"] <- video_details_list[[i]]$video_details$result$items[[1]]$snippet$description
    video_df[i, "video_tags"] <- paste(video_details_list[[i]]$video_details$result$items[[1]]$snippet$tags, collapse = " ")
    video_df[i, "video_transcript"] <- ifelse(!is.null(video_details_list[[i]]$video_captions$result), rawToChar(video_details_list[[i]]$video_captions$result), "")
    video_df[i, "video_comments"] <- ifelse(!is.null(video_details_list[[i]]$video_comments$result), paste(video_details_list[[i]]$video_comments$result$textOriginal, collapse = " ")) # HOW TO PASTE COMMENTS TOGETHER?
  }
  
  video_df
}

video_data <- simplify_video_details(video_details[-1])

# Save local buffer data
saveRDS(video_data, file = "video_data.rds")

head(video_data)
```

## Generate documents

All channel and video details need to be combined in a corpus to be analysed.

# Documents and features

# Preprocessing of text

```{r}

# Preprocess text
video_data$video_transcript <- str_replace_all(video_data$video_transcript, pattern = "(\\n\\n)*\\d\\:\\d{2}\\:\\d{2}\\.\\d{3}\\,\\d\\:\\d{2}\\:\\d{2}\\.\\d{3}\\n", replacement = "") # Remove subtitle time codes
str_replace_all(video_data$video_transcript, pattern = "\\.\\.\\.", replacement = "") # Remove ...

# Construct documents (all text from channel details and videos within that channel)
generate_channel_documents <- function(channel_data_df, video_data_df){
  
  channel_doc_df <- data.frame(stringsAsFactors = FALSE)
  
  # Generate videos texts column
  videos_texts <- vector(mode = "character", length = length(channel_data_df))
  
  # Generate videos texts for each channel row
  for(i in seq_along(channel_data_df$channel_id)){
    
    # Select all videos in this channel
    channel_videos <- channel_videos_df[channel_videos_df$channel_id == channel_data_df$channel_id[i], ]$video_id
    print("Channel videos:")
    print(channel_videos)
    
    videos_texts[[i]] <- as.character(paste(video_data_df[video_data_df$video_id %in% channel_videos, -1], collapse = " ")) # Pasting creates three concatenations...
    print("Video texts:")
    print(videos_texts[[i]])
  }
  
  # Merge videos texts column
  channel_doc_df <- cbind(channel_data_df, videos_texts)
  channel_doc_df$videos_texts <- as.character(channel_doc_df$videos_texts)
  
  # Return channel document data frame
  channel_doc_df
}

left_channel_docs <- generate_channel_documents(left_channels_data, video_data)
#right_channel_docs <- generate_channel_documents(right_channels_data, video_data)
```

## Generate corpus

## Topic exploration


```{r}
# Generate corpus
quanteda_options("threads" = 10)
left_corpus <- corpus(left_channel_docs, docid_field = "channel_id", text_field = "videos_texts")
right_corpus <- corpus(right_channel_docs, docid_field = "channel_id", text_field = "videos_texts")

# Generate DFMs
left_dfm <- dfm(left_corpus, remove_punct = TRUE, remove = stopwords('en')) # %>%
            # dfm_trim(min_termfreq = 0.95, termfreq_type = "quantile", 
            #          max_docfreq = 0.1, docfreq_type = "prop")
left_dfm <- left_dfm[ntoken(left_dfm) > 0,]

right_dfm <- dfm(right_corpus, remove_punct = TRUE, remove = stopwords('en')) #%>%
            # dfm_trim(min_termfreq = 0.95, termfreq_type = "quantile", 
            #          max_docfreq = 0.1, docfreq_type = "prop")
right_dfm <- right_dfm[ntoken(right_dfm) > 0,]

# Create LDA topic model
left_dtm <- convert(left_dfm, to = "topicmodels")
left_lda <- LDA(left_dtm, k = 10)

right_dtm <- convert(right_dfm, to = "topicmodels")
right_lda <- LDA(right_dtm, k = 10)

# List topic terms
left_topic_terms <- terms(left_lda, 10)
print("Left topic terms:")
print(left_topic_terms)

right_topic_terms <- terms(right_lda, 10)
print("Right topic terms:")
print(right_topic_terms)

print(Sys.time())
```

## Clustering of extreme content

When unsupervised clustering into two groups based on text; do we see a similar division as the left-right distinction we made.








## Sentiment analysis of comments

How to translate?

## Analysis of sources

Analyse channel featured sources

## Analysis of name-entities

Extract websites, names, channels, users


## Recommendation research

### Test the hunch that recommendations lead to more extreme content
50 subjects were students (MBO, HBO) and that most of them don’t describe themselves as politically interested. It’s therefore very interesting to see what happens if they start looking for information on politically sensitive issues.
We tweaked a script from Guillaume Chaslot, build an executable and asked subjects to run the script from their computer. We have used ten queries that were used to search YouTube and then clicked on the recommendations (depth 4). The search terms were:
Geert Wilders, Sylvana Simons, Thierry Baudet, Kajsa Ollongren, Feminisme, Holocaust, Zwarte Piet, Eurocrisis, Islam, Vluchtelingen.

```{r}
# recommendation_files  <- list.files(path = "Local extremism data/raw/recommendations/resultaten_yt", pattern = "youtube-", recursive = TRUE)
# recommendation_file_paths <- paste0("Local extremism data/raw/recommendations/resultaten_yt/", recommendation_files)
# 
# recommendation_jsons <- lapply(recommendation_file_paths[1:100], FUN = function(x) stream_in(file(x))) # Please note this is just a subset due to parsing errors due tro truncation of file path name in wondows.
# 
# recommendation_files_meta <- as_data_frame(recommendation_files %>%
#                                 str_replace_all(pattern = "youtube-win-\\s?|youtube-onderzoek-mac-\\s?", replacement = "") %>%
#                                 str_replace("-", " ") %>%
#                                 str_replace("\\.json", "")) %>%
#                                 separate(value, into = c("user_hash", "search"), sep = "/") %>%
#                                 separate(search, into = c("search_string", "date"), sep = -10) %>%
#                                 mutate(search_string = str_sub(search_string, 1, -2))
# head(recommendation_files_meta) %>%
#                                 mutate(date = as.Date(date))
  
```


## Comparing November 2017 with August 2018
### Test the claim of YouTube removing extreme content.

```{r}
# # November 2017 data
# november_nodes <- read_csv("Local extremism data/graphs/network_november_2017/yt_node_table_depth1_v3.csv")
# november_edges <- read_csv("Local extremism data/graphs/network_november_2017/yt_edge_table_depth1_v3.csv")
# november_network_nosubs <- read_gdf("Local extremism data/graphs/network_november_2017/yt_depth1_without_subscriptions_v2.gdf")
# november_network_subs <- read_gdf("Local extremism data/graphs/network_november_2017/yt_depth1_with_subscriptions_v2.gdf")
# 
# # trying to plot gdfs [IN PROGRESS]
# interactive_graph_data <- igraph_to_networkD3(november_network_nosubs)
# interactive_graph <- simpleNetwork(interactive_graph_data)
# 
# # August 2018 data
# august_network_subs <- read_gdf("Local extremism data/graphs/network_august_2018/yt_depth1_with_subscriptions_v1_august_2018.gdf")
```

